Classless Java: Tuning Java Interfaces

### 2015-12-08 paper/sections/Formalization.tex
small fixes
revise the newly added example

\subsection{Methods in Java 8 Interfaces}
In Java 8 interfaces there are three types of methods: abstract, default, and
static methods.

@@

\paragraph{Example}
To illustrate the mechanism of $\mBody$ in a clearer and more intuitive way, we present an example here.
\begin{lstlisting}
interface A { Object m(); }
interface B extends A { default Object m() {return new Object(){};} }
interface C extends A {}
interface D extends B, C { String m(); }
\end{lstlisting}
We start to compute $\mBody(\QM{m},\QM{D})$ inside out, and step by step:
\begin{itemize}
\item First the full set of supertypes of $\QM{D}$ is obtained recursively and results in $\{\QM{A,B,C}\}$.
\item To compute $\tops(\QM{m},\{\QM{A,B,C}\})$, $\QM{C}$ can be omitted, since $\QM{m}$ is not declared directly in $\QM{C}$, hence $\Aux{originalMethod}(\QM{m},\QM{C})$ is undefined. And $\QM{B}$ is a subtype of $\QM{A}$ (thus $\QM{B.m}$ hides $\QM{A.m}$), so $\tops(\QM{m},\{\QM{A,B,C}\})$ equals $\QM{B.m}$.
\item Now the final step is to compute $\override(\QM{D.m},\QM{B.m})$, and this concludes by the fifth case of $\override$ that $\QM{D.m}$ hides $\QM{B.m}$ successfully ($\QM{String}$ is a subtype of $\QM{Object}$) and becomes the most specific method. So finally we get $\mBody(\QM{m},\QM{D}) = \QM{D.m}$.
\end{itemize}
%The \textsf{shadow} function takes two same methods (with the same name and types of arguments), and return the method which shadows the other during inheritance.
%exmples to motivate our design
%interface A{static String m(){return "A";}}
%interface C extends A{
%	default String dm(){
%		  this.m();//wrong in java
%		  A.m();
%		  C.m();//wrong in java
%		}
%}
%
%
%(1) Static methods are not inherited. Also, if one of $\{body_1,body_2\}$ is null, \textsf{shadow} simply returns the other one. Hence

>>>>

\subsection{Methods in Java 8 Interfaces}
In Java 8 interfaces there are three types of methods: abstract, default, and static methods. Default and static methods were not allowed in interfaces in previous versions of Java.

@@

\paragraph{Example}
To illustrate the mechanism of $\mBody$ in a more intuitive way, we present an example here.
\begin{lstlisting}
interface A { Object m(); }
interface B extends A { default Object m() {return new Object(){};} }
interface C extends A {}
interface D extends B, C { String m(); }
\end{lstlisting}
We start to compute $\mBody(\QM{m},\QM{D})$ inside out, and step by step:
\begin{itemize}
\item First the full set of supertypes of $\QM{D}$ is obtained recursively and results in $\{\QM{A,B,C}\}$.
\item To compute $\tops(\QM{m},\{\QM{A,B,C}\})$, $\QM{C}$ will be omitted, since $\QM{m}$ is not declared directly in $\QM{C}$, hence $\Aux{originalMethod}(\QM{m},\QM{C})$ is undefined. And $\QM{B}$ is a subtype of $\QM{A}$ (thus $\QM{B.m}$ hides $\QM{A.m}$), so $\tops(\QM{m},\{\QM{A,B,C}\})$ equals $\QM{B.m}$.
\item The final step is to compute $\override(\QM{D.m},\QM{B.m})$, and this matches the fifth case of $\override$ that $\QM{D.m}$ hides $\QM{B.m}$ successfully ($\QM{String}$ is a subtype of $\QM{Object}$) and becomes the most specific method. So finally we get $\mBody(\QM{m},\QM{D}) = \QM{D.m}$.
\end{itemize}
%The \textsf{shadow} function takes two same methods (with the same name and types of arguments), and return the method which shadows the other during inheritance.
%exmples to motivate our design
%interface A{static String m(){return "A";}}
%interface C extends A{
%	default String dm(){
%		  this.m();//wrong in java
%		  A.m();
%		  C.m();//wrong in java
%		}
%}
%
%
%(1) Static methods are not inherited. Also, if one of $\{body_1,body_2\}$ is null, \textsf{shadow} simply returns the other one. Hence
